What paradigms can webcam eye-tracking be used for? Attempted replications of 5 ``classic'' cognitive science experiments

### 2024-02-17 group-a/E1-analysis-calibration.Rmd
fixes to get figures to display and cross-ref correctly

```{r}
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent").
```
<!-- # Setup -->
```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source('round.comm.R')

>>>>

<!-- # Setup 
#To be run after E1-analysis-replication.Rmd
#Correlates subjects' experimental effects with their calibration quality (from df called "validation.percent"). -->
```{r E1-c-setup, message=FALSE, warning=FALSE, include = FALSE, echo = FALSE}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(readr)
library(afex)
library(forcats)
library(papaja)
source('round.comm.R')

### 2024-02-17 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
fixes to get figures to display and cross-ref correctly

#### Cumulative Fixation Probabilities
For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later. This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin. Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure \@ref(fig:jh-E1-spaghetti-fig).

```{r jh-E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."} 
jh.E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
  geom_vline(xintercept = mean(jh.word.dur.avg$Total))

jh.E1_spag_fig

>>>>

#### Cumulative Fixation Probabilities
For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later. This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin. Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1-JH-spaghetti-fig).

```{r E1-JH-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

jh_E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
  geom_vline(xintercept = mean(jh.word.dur.avg$Total))

jh_E1_spag_fig

### 2024-02-17 group-a/E1-analysis-replication.Rmd
fixes to get figures to display and cross-ref correctly

```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."} 
E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
  geom_line()+
  geom_point(size=2, aes(fill=object_class, shape=verb_type))+
  #scale_fill_grey(start=1.0, end=0.0)+
  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"))+
  scale_shape_manual(name = "Verb Type", values=c(22,21))+
  labs(x="Time from Verb Onset (ms)", y="Probability")+#, shape="Verb Type", fill="Object Type")+
  #geom_line(aes(group=interaction(verb_type, object_class)))+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  geom_vline(xintercept = mean(word.dur.avg$Total))

@@

>>>>

```{r E1-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

E1_spag_fig <- ggplot(cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill= object_class, shape=verb_type))+
  geom_line()+
  geom_point(size=2, aes(fill=object_class, shape=verb_type))+
  #scale_fill_grey(start=1.0, end=0.0)+
  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"))+
  scale_shape_manual(name = "Verb Type", values=c(22,21))+
  labs(x="Time from Verb Onset (ms)", y="Probability")+#, shape="Verb Type", fill="Object Type")+
  #geom_line(aes(group=interaction(verb_type, object_class)))+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  geom_vline(xintercept = mean(word.dur.avg$Total))

@@

```{r Load data}
# load("pre.noun.first.looks.data.min.RData") 
# load("pre.verb.offset.first.looks.data.min.RData")
# load("first.fixation.after.verb.onset.analysis.data.min.RData")
# load("validation.percent.RData")
# load("first.fixation.after.verb.onset.subject.summary.min.RData")

pre.noun.first.looks.data <- pre.noun.first.looks.data.min
pre.verb.offset.first.looks.data <- pre.verb.offset.first.looks.data.min
first.fixation.after.verb.onset.analysis.data <- first.fixation.after.verb.onset.analysis.data.min
first.fixation.after.verb.onset.subject.summary <- first.fixation.after.verb.onset.subject.summary.min  
```

```{r Model 1 subject summary}
pre.noun.subj.summary <- pre.noun.first.looks.data %>%
  group_by(subject_id, verb_type, object_class) %>%
  summarize(fix.p = mean(cumulative.fixation.p))

pre.noun.by.verb <- pre.noun.subj.summary %>%
  pivot_wider(names_from = object_class, values_from = fix.p) %>%
  mutate(tar.adv = target.object - distractor)

pre.noun.effects <- pre.noun.by.verb %>%
  select(subject_id, verb_type, tar.adv) %>%
  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(effect = restricting - non_restricting)
```

```{r Model 1 effect size by calibration}
#merge with validation percent

cali.analy.1 <- merge(pre.noun.effects, validation.percent, by = "subject_id")

#correlate
m1_diffdiff_cor <- cor.test(cali.analy.1$effect, cali.analy.1$M, use = "pairwise.complete.obs") #difference of differences
#0.03107354
m1_diffdiff_cor_r <- m1_diffdiff_cor$estimate
m1_diffdiff_cor_p <- m1_diffdiff_cor$p.value

m1_diff_cor <- cor.test(cali.analy.1$restricting, cali.analy.1$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
#0.2096605
m1_diff_cor_r <- m1_diff_cor$estimate
m1_diff_cor_p <- m1_diff_cor$p.value
```

```{r Model 2 subject summary}
pre.verb.subj.summary <- pre.verb.offset.first.looks.data %>%
  group_by(subject_id, verb_type, object_class) %>%
  summarize(fix.p = mean(cumulative.fixation.p))

pre.verb.by.verb <- pre.verb.subj.summary %>%
  pivot_wider(names_from = object_class, values_from = fix.p) %>%
  mutate(tar.adv = target.object - distractor)

pre.verb.effects <- pre.verb.by.verb %>%
  select(subject_id, verb_type, tar.adv) %>%
  pivot_wider(names_from = verb_type, values_from = tar.adv) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(effect = restricting - non_restricting)
```

```{r Model 2 effect size by calibration}
#merge with validation percent
cali.analy.2 <- merge(pre.verb.effects, validation.percent, by = "subject_id")

#correlate
m2_diffdiff_cor <- cor.test(cali.analy.2$effect, cali.analy.2$M, use = "pairwise.complete.obs") #difference of differences
#-0.04809241
m2_diffdiff_cor_r <- m2_diffdiff_cor$estimate
m2_diffdiff_cor_p <- m2_diffdiff_cor$p.value

m2_diff_cor <- cor.test(cali.analy.2$restricting, cali.analy.2$M, use = "pairwise.complete.obs") #target adv. in restricting condition only
#-0.03601876
m2_diff_cor_r <- m2_diff_cor$estimate
m2_diff_cor_p <- m2_diff_cor$p.value

```{r Model 3 effect size by calibration}
#summary(validation.percent)
#make looking scores for Ps
looking.scores <- first.fixation.after.verb.onset.subject.summary[,1:3] %>% 
  spread(verb_type, m.t) %>%
  rename("non_restricting" = "non-restricting") %>%
  mutate(diff = non_restricting - restricting)

#merge with validation percent
cali.analy.3 <- merge(looking.scores, validation.percent, by = "subject_id")

#correlate
m3_diff_cor <- cor.test(cali.analy.3$diff, cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
m3_diff_cor_r <- m3_diff_cor$estimate
m3_diff_cor_p <- m3_diff_cor$p.value
```

#### Calibration
Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality varied widely, ranging from `r min(validation.percent$M) %>% round(digits = 2)`% to `r max(validation.percent$M) %>% round(digits = 2)`%.

We tested whether a participant's calibration quality was correlated with their effect size. There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions). Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`. However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e. rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r m1_diff_cor_r`, _p_ = `r m1_diff_cor_p`).

### 2024-02-17 group-a/E1-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 1. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

The task began with a 9-point eye-tracker calibration
and validation (Figure\ \@ref(fig:E1-calibration-figure)). 
During the experiment, the participants were
simultaneously presented with a visual image and a corresponding audio
recording of a spoken sentence. Participants had to input a keyboard
response indicating "yes" or "no" as to whether the sentence they heard
was feasible given the visual image. There were two practice trials to
ensure that participants understood the instructions
before they undertook the main portion of the experiment. Participants'
reaction times, keyboard responses, and looks to objects in the scene
were recorded for each trial.

@@

```{r E1-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 1. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2024-02-17 group-b/E2-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 2. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

The task began with a 9-point eye-tracker calibration
and validation (Figure \@ref(fig:E2-calibration-figure)).

@@

```{r E2-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 2. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2024-02-17 group-c/E3-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

The task began with a 7-point eye-tracker calibration (each point was
presented 3 times in a random order) and validation with 3 points (each
presented once). The point locations were designed to focus calibration
on the center of the screen and the middle of the left and right halves
of the screen (Figure\ \@ref(fig:E3-calibration-figure)).

@@

```{r E3-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 3. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2024-02-17 group-d/E4-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 4. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

After the eye-tracking calibration and validation (Figure\ \@ref(fig:E4-calibration-figure)), participants went through an audio
test so they could adjust the audio on their computer to a comfortable
level. Before beginning the experiment, they were given instructions
that four objects would appear, an audio prompt would play, and they
should do their best to use their mouse to act out the instructions.
They then went through three practice trials which were followed by 54
critical trials and 24 filler trials presented in a random order.

@@

```{r E4-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 4. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.(In this experiment all the same locations were used for both calibration and validation.)", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2024-02-17 group-e/E5-calibration-figure.Rmd
fixes to get figures to display and cross-ref correctly

@@

```{r echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 5. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

>>>>

At the beginning of the experimental task, participants completed a
9-point eye-tracker calibration (each point appeared 3 times in random
order) and 3-point validation. The validation point appeared once at
center, middle left, and middle right locations in random order (see Figure\ \@ref(fig:E5-calibration-figure)).
<!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total? If the latter, why is the coverage denser than for Experiment 4? -->

@@

```{r E5-calibration-figure, echo=FALSE, fig.cap="Calibration and validation point locations for Experiment 5. Black points were used for calibration. Red crosses were used for checking the accuracy of the calibration.", fig.width=6, fig.height=4}
ggplot(df, aes(x=x, y=y, shape=point, color=point))+
  geom_point(size=3, stroke=1)+
  scale_shape_manual(values=c(16,3))+
  scale_color_manual(values=c("black", "red"))+
  coord_cartesian(xlim=c(0,100), ylim=c(100,0), expand=FALSE)+
  theme_void()+
  labs(color=NULL, shape=NULL)+
  theme(panel.border = element_rect(color="black", fill=NA),
        legend.position = c(0.995,0.01),
        legend.justification = c(1,0),
        legend.background = element_rect(color="black", fill=NA),
        legend.margin = margin(2,3,3,3))
```

### 2024-02-17 manuscript.Rmd
fixes to get figures to display and cross-ref correctly

The task began with a 9-point eye-tracker calibration
and validation (Figure\ \@ref(fig:E1-calibration-figure) ). 
During the experiment, the participants were
simultaneously presented with a visual image and a corresponding audio
recording of a spoken sentence. Participants had to input a keyboard
response indicating "yes" or "no" as to whether the sentence they heard
was feasible given the visual image. There were two practice trials to
ensure that participants understood the instructions
before they undertook the main portion of the experiment. Participants'
reaction times, keyboard responses, and looks to objects in the scene
were recorded for each trial.

```{r E1-calibration-figure, child='group-a/E1-calibration-figure.Rmd'}

@@

```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
```

### In-lab sample
```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}
#Includes calibration analysis 
```

@@

The task began with a 9-point eye-tracker calibration
and validation (Figure\ \@ref(fig:E2-calibration-figure)).

```{r E2-calibration-figure, child='group-b/E2-calibration-figure.Rmd'}

@@

The task began with a 7-point eye-tracker calibration (each point was
presented 3 times in a random order) and validation with 3 points (each
presented once). The point locations were designed to focus calibration
on the center of the screen and the middle of the left and right halves
of the screen (Figure\ \@ref(fig:E3-calibration-figure)).

```{r E3-calibration-figure, child='group-c/E3-calibration-figure.Rmd'}

@@

After the eye-tracking calibration and validation (Figure\ \@ref(fig:E4-calibration-figure)), participants went through an audio
test so they could adjust the audio on their computer to a comfortable
level. Before beginning the experiment, they were given instructions
that four objects would appear, an audio prompt would play, and they
should do their best to use their mouse to act out the instructions.
They then went through three practice trials which were followed by 54
critical trials and 24 filler trials presented in a random order.

```{r E4-calibration-figure, child='group-d/E4-calibration-figure.Rmd'}

@@

At the beginning of the experimental task, participants completed a
9-point eye-tracker calibration (each point appeared 3 times in random
order) and 3-point validation. The validation point appeared once at
center, middle left, and middle right locations in random order (see Figure\ \@ref(fig:E5-calibration-figure)).
<!-- does 9 points here mean that there were actually only 3 calibration points but each was shown 3 times so 9 total or is it 9 points shown 3 times so 27 total? If the latter, why is the coverage denser than for Experiment 4? -->
```{r E5-calibration-figure, child='group-e/E5-calibration-figure.Rmd'}

@@

We conducted 5 attempted replication studies using different experimental paradigms from across the cognitive sciences. All were successfully implemented in `jsPsych` using the `webgazer` plugin, but replication success was mixed. Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with 5 to 6 ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants. Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [@james2023language]. A previous conceptual replication of this paradigm using webcam-based eye-tracking [prystauka2023online] was successful but used a 4-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts. It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm. The primary limitation is likely to be the size of the ROIs.

@@

Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask200. However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test. Calibration quality did not appear to impact this relationship. More work is needed to understand whether delay manipulations can be practically combined with webcam eye-tracking.

>>>>

```{r E1 calibration figure, child = 'group-a/E1-calibration-figure.Rmd' }

@@

<!---```{r E1-analysis-calibration, child = 'group-a/E1-analysis-calibration.Rmd'}
# the presence of this chunk separate from the replication analysis was somehow causing the figures to disappear so I copied the calibration rmd content into the analysis-replication rmd and this solved the problem.
```--->

### In-lab sample

<!---
test figure \@ref(fig:test)

```{r test, fig.cap = "test plot"}

plot(cars$speed, cars$dist)

```
--->

```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}

@@

```{r E2 calibration figure, child='group-b/E2-calibration-figure.Rmd'}

@@

```{r E3 calibration figure, child='group-c/E3-calibration-figure.Rmd'}

@@

```{r E4 calibration figure, child='group-d/E4-calibration-figure.Rmd'}

@@

```{r E5 calibration figure, child='group-e/E5-calibration-figure.Rmd'}

@@

We conducted 5 attempted replication studies using different experimental paradigms from across the cognitive sciences. All were successfully implemented in `jsPsych` using the `webgazer` plugin, but replication success was mixed. Experiment 1 had the smallest ROIs due to the use of an integrated visual scene with 5 to 6 ROIs of varying size per scene, as opposed to ROIs corresponding to display halves or quadrants. Both attempts to replicate @altmannIncrementalInterpretationVerbs1999 were unsuccessful, despite the success of previous in-lab replications using infrared eye-tracking [@james2023language]. A previous conceptual replication of this paradigm using webcam-based eye-tracking [@prystauka2023online] was successful but used a 4-quadrant visual world paradigm, rather than the "naturalistic" scenes used in the original study and in the current replication attempts. It is worth noting that removing variability related to participant environments (by conducting the webcam-tracking study in the lab) did not appear to improve the sensitivity of the paradigm. The primary limitation is likely to be the size of the ROIs.

@@

Experiment 3 used 2 large ROIs (halves of the display in one analysis) and successfully replicated the novelty preference in terms of gaze duration shown in @mannsVisualPairedcomparisonTask2000. However, the subtler relationship between gaze duration and recognition memory on day 2 was not replicated, despite the fact that participants were able to discriminate pictures they had seen from those they hadn't seen during that delayed test. Calibration quality did not appear to impact this relationship. More work is needed to understand whether delay manipulations can be practically combined with webcam eye-tracking.
